Holomorphic M-theory and the $\SU(4)$-invariant twist of type $\IIA$

### 2020-10-14 oldstuff/BCOV with potentials/BCOV with potentials.tex
update2

% Created 2020-08-18 Tue 22:24
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{macros}
\usepackage{tikz,tikz-cd}
\newcommand{\surya}[1]{(\textcolor{red}{Surya: #1})}
\newcommand{\brian}[1]{(\textcolor{blue}{Brian: #1})}
%brian's macros
\newcommand\bu{\bullet}
\newcommand\dbar{\overline{\partial}}

@@

Let $X$ be a Calabi--Yau surface. 
Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded Poisson BV theory described by two fundamental sets of fields:
\begin{itemize}
\item An odd field given by a divergence-free holomorphic vector field $\mu^1$. 
\item An even field given by a holomorphic function $\mu^0$.
\end{itemize}
These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.

The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} \\
 & \PV^{0,\bu} \\
 \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
\end{tikzcd}
\]
We refer to this locally free description by $\mc E$. 
The Lie bracket on $\Pi \mc E^{\rm hol}$ described above extends to a Lie bracket on $\Pi \mc E$.
Together with the differential this gives $\Pi \mc E$ the structure of a local dg Lie algebra.

The bundle $\mc E$ is equipped with an odd Poisson tensor defined by 
\[
\Pi = (\partial \otimes 1) \delta_{\rm Diag} .
\]

@@

We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way. 
There is a map of bundles $\Phi : \mc E_{\rm Pot} \to \mc E$ which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes.

@@

@@

Finally, the theory $\mc E_{\rm pot}$ is a non-degenerate BV theory with BV pairing defined by the wedge-and-integrate pairing
\[
\alpha, \beta \mapsto \int \alpha \wedge \beta  .
\]

\begin{prop}
The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
\[
\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
\]
\end{prop}

@@

There is a local Lie algebra structure on $\Pi\mc E$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
On the fields (including the descendants) it is defined by the formula
\[
[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} [\mu^i, \mu^j]_{\rm Sch} .
\]

Furthermore, the sheaf $\mc E$ is equipped with an odd Poisson tensor given by $\Pi = (\del\otimes 1)\delta_{\rm Diag}$. Together, this data equips $\mc E$ with the structure of a $\Z/2$-graded Poisson BV theory.

As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
The underlying sheaf of cochain complexes is 
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \mu^{0}\in\PV^{0,\bu} \\
& & \sum u^k \mu^{1}\in\PV^{1,\bu} \ar[r, "\partial"] & \mu^{c}\in\PV^{0,\bu} \\
u^{-1} \gamma^3 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
\gamma^{4} \in\PV^{4,\bu} &  &  & \\
\end{tikzcd}
\]
We will again refer to this sheaf as $\mc E_{\rm pot}$.

There is a local Lie algebra structure described as follows.
\brian{It's mostly the Schouten bracket, but there is the additional ``weird" bracket
\[
[\gamma^3, \gamma^{3'}] = [\partial \gamma^3 , \gamma^{3'}] \pm [\gamma^3, \partial \gamma^{3'}] .
\]
}

There is a map of sheaves of cochain complexes $\Phi: \mc E_{\rm pot}\to \mc E$ given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$. 
Explicitly, in formulas
\[
\begin{array}{ccccccccc}
\Phi(t^k \mu^{i}) & = & u^k \mu^i & \in & u^k \PV^{i, \bu} & i = 0,1 \\
\Phi(u^{-1} \gamma^3) & = & 0 \\
\Phi(\gamma^3) & = & \partial \gamma^3 & \in & \PV^{2,\bu} \\
\Phi(\gamma^4) & = & \partial \gamma^4 & \in & \PV^{3,\bu} .
\end{array} 
\]

@@

In fact, we have the following, analogous to the case of a Calabi-Yau surface:
\begin{prop}
The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
\[
\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
\]
\end{prop}

@@

The fields decompose as follows.
For the ``base" direction, fields we labeled by $\mu$, we have
\[
\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ \oplus & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
\]

For the ``fiber" direction, fields we labeled by $\gamma$, we have
\[
\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ \oplus & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
\]

The ``zero modes" of the reduction along the circle $S^1 \subset \mb C^\times$ will be denoted by the same symbols.
\brian{write down this sheaf on $\mb C^4 \times \mb R^2$.}

Define the map of sheaves of cochain complexes 
\[
\Psi : \pi_* \mc E_{11d} \to \mc E_{\rm pot} \Hat{\otimes} \Omega^\bu(\mb R^2) 
\] 
by
\[
\begin{array}{cccccccc}
\Psi (\mu_{01}) & = & \mu_{01} & \in & \PV^{1,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\
\Psi (\mu_{10}) & = & \mu_{10} \vee \Omega^{-1}_{\mb C^4} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) .
\end{array}
\]

@@

\begin{prop}
There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\otimes\mc E_{Pot}$ given by
\begin{itemize}
\item $[\gamma_{10}]\mapsto\mu^0\in\PV^{0,\bullet}\subset\mc E_{Pot}$.
  \item $[\mu_{01}]\mapsto\mu^1\in\PV^{1,\bullet}(\C^4)\subset\mc E_{Pot}$.
\item $[\mu^{0}]\mapsto\mu^{c}\in\PV^{0, \bullet}(\C^{4})\subset\mc E_{Pot}$.
\item $[\gamma_{01}]\mapsto\mu^3 = \gamma_{01}\vee\Omega^{-1}_{\C^4}\in\PV^{3,\bullet}\subset\mc E_{Pot}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
\item $[\mu_{10}]\mapsto\mu^4 =\mu_{10}\vee\Omega^{-1}_{\C^4}\in\PV^{4,\bullet}\subset\mc E_{Pot}$ .

\end{itemize}
preserving the relevant pairings.
\end{prop}

@@

\begin{rmk}
Note that the field $\mu^{c}\in \mc E_{\mr Pot}$ is nonpropating. It must pair against a field in $\PV^{3}$. In order for the field $\mu^{0}$ in M-theory to propagate, it must pair against a field $\gamma^{0}\in \Omega^{0,\bullet}$ which is the ghost for the gauge transformation for $\gamma^{1}$. This suggests an enlargement of $\mc E_{\mr Pot}$ where we add an additional field in $\PV^{3}$ which will be the image of the ghost of $\gamma^{1}$ in M-theory under dimensional reduction.
\end{rmk}

\surya{ When we discussewd dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$. I realized this was wrong - the resulting map cannot be a Lie map. Indeed, there is certainly a nontrivial bracket between $\gamma_{10}$ and $\gamma_{10}$ in M-theory, from expanding the $\gamma\del\gamma\del\gamma$ term. However, there is no nontrivial bracket between $\PV^{3,\bullet}$ and $\PV^{4,\bullet}$ in $\mc E_{\rm Pot}$ }

>>>>

% Created 2020-08-18 Tue 22:24
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{macros}
\usepackage{tikz,tikz-cd}
\newcommand{\surya}[1]{(\textcolor{red}{Surya: #1})}
\newcommand{\brian}[1]{(\textcolor{blue}{Brian: #1})}
%brian's macros
\newcommand\bu{\bullet}
\newcommand\dbar{\overline{\partial}}
\newcommand\CC{{\mb C}}
\newcommand \RR{{\mb R}}
\def\Hat{\widehat}

@@

On a Calabi--Yau surface $X$, minimal Kodaira--Spencer theory is the $\mb Z/2$-graded theory described by two fundamental sets of fields:
\begin{itemize}
\item An odd field given by a divergence-free holomorphic vector field $\mu^1$. 
\item An even field given by a holomorphic function $\mu^0$.
\end{itemize}
%These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
%There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.

%The sheaf $\mc E^{\rm hol}$ admits the following locally free description:

In the BV formalism, minimal Kodaira--Spencer theory on $X$ is a (degenerate) Poisson BV theory with space of fields given by
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} \\
 & \PV^{0,\bu} \\
 \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
\end{tikzcd}
\]
We will denote this sheaf of $\mb Z/2$-graded cochain complexes by $\mc E_{\rm KS}$.

There is a local (dg) Lie algebra structure on the parity shifted object $\Pi \mc E_{\rm KS}$. 
The Lie bracket is defined using the Schouten-Nijenhuis bracket $[-,-]_{\rm NS}$ on polyvector fields and is given by the formula
\[
[u^k \alpha , u^\ell \beta] = u^{k+\ell} [\alpha, \beta]_{\rm NS} .
\]
where $k, \ell = 0,1$.
Together with the differential this equips the parity shifted sheaf of cochain complexes $\Pi \mc E_{\rm KS}$ with the structure of a local (dg) Lie algebra.

The fields of minimal Kodaira--Spencer theory $\mc E_{\rm KS}$ is equipped with an odd Poisson tensor defined by 
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]

@@

We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way. 
There is a map of sheaves of cochani complexes 
\[
\Phi : \mc E_{\rm Pot} \to \mc E_{\rm KS}
\]
which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes. 
The theory $\mc E_{\rm pot}$ is equipped with a non-degenerate BV pairing defined by the wedge-and-integrate pairing
\[
\omega_{\rm pot} (\alpha, \beta) = \int \alpha \wedge \beta  .
\]
It is immediate to verify that $\Phi$ intertwines the resulting bivector $\omega_{\rm pot}^{-1}$ and the Kodaira--Spencer Poisson bivector $\Pi_{\rm KS}$.

@@

This equipped $\mc E_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory. 
It's relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.

@@

\begin{prop}
The map $\Phi : \mc E_{\rm pot} \to \mc E_{\rm KS}$ determines a map of $\mb P_0$-factorization algebras on $X$:
\[
\Phi^* : {\rm Obs}_{\mc E_{\rm KS}} \to {\rm Obs}_{\mc E_{\rm Pot}} .
\]
\end{prop}

@@

There is a local Lie algebra structure on $\Pi\mc E$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
On the fields (including the descendants) it is defined by the formula
\[
[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} [\mu^i, \mu^j]_{\rm NS} .
\]

The space of fields of minimal Kodaira--Spencer theory $\mc E_{\rm KS}$ is equipped with an odd Poisson tensor defined by 
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]
Together with the local Lie algebra structure, this data equips $\mc E$ with the structure of a $\Z/2$-graded Poisson BV theory.

As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
The underlying sheaf of cochain complexes is 
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \mu^{0}\in\PV^{0,\bu} \\
& & \sum u^k \mu^{1}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
u^{-1} \gamma^3 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
\gamma^{4} \in\PV^{4,\bu} &  &  & \\
\end{tikzcd}
\]
We will again refer to this sheaf as $\mc E_{\rm pot}$.

There is a local Lie algebra structure described as follows.
\begin{itemize}
\item 
There is a self bracket between the $\mu$-fields defined by
\[
[u^k \mu^i, u^\ell \Tilde{\mu}^j] = u^{k+j} [\mu^i, \Tilde{\mu}^j]_{\rm NS} .
\]
\item Next, there is a self-bracket between the $\gamma$-fields defined by 
\[
[\gamma^3, \Tilde{\gamma}^3] = [\partial \gamma^3 , \Tilde{\gamma}^{3}]_{\rm NS} \pm [\gamma^3, \partial \Tilde{\gamma}^{3}]_{\rm NS} \in {\rm PV}^{4,\bu} 
\]
\item Finally, there are mixed terms in the bracket defined by
\[
[u^{-k} \gamma^i , u^\ell \mu^j] = u^{-k + \ell} [\partial \gamma^i, \mu^j]_{\rm NS}
\]
\end{itemize}

Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes 
\[
\Phi: \mc E_{\rm pot}\to \mc E_{\rm KS} .
\] 
It is given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$. 
Explicitly, in formulas
\[
\arraycolsep=1.4pt\def\arraystretch{2.2}
\begin{array}{ccccccccc}
\Phi(u^k \mu^{i}) & = & u^k \mu^i & \in & u^k \PV^{i, \bu} & i = 0,1 \\
\Phi(u^{-1} \gamma^3) & = & 0 \\
\Phi(\gamma^3) & = & \partial \gamma^3 & \in & \PV^{2,\bu} \\
\Phi(\gamma^4) & = & \partial \gamma^4 & \in & \PV^{3,\bu} .
\end{array} 
\]

@@

In fact, we have the following result, in analogy with the case of a Calabi-Yau surface.

\begin{prop}
The map $\Phi$ intertwines the local Lie algebra structures and Poisson BV structures on $\mc E_{\rm KS}$ and $\mc E_{\rm pot}$. 
So, it induces a map of $\mb P_0$-factorization algebras:
\[
\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
\]
\end{prop}

@@

The fields decompose as follows.
For the ``base'' direction, fields we labeled by $\mu$, we have
\[
\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
\]

For the ``fiber'' direction, fields we labeled by $\gamma$, we have
\[
\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
\]

We consider the dimensional reduction of the theory along the circle $S^1 \subset \mb C^\times$.
The dimensional reduction has the affect of replacing $\PV^{i,\bu}(\mb C^\times)$ and $\Omega^{1,\bu}(\mb C^\times)$ by the de Rham along the radial direction in $\mb C^\times$, see Proposition 1.59 of \cite{ESW}. 
Denote the space of fields of the dimensional reduction by $\oint_{S^1} \mc E_{11d}$.

We will use the same symbols for the fields in the dimensionally reduced ten-dimensional theory: for the dimensionally reduced $\mu$-fields we have
\[
\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{1,\bullet}(\C^4) \\ & \PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R^2) [1] .
\]
and for the dimensionally reduced $\gamma$-fields we have
\[
\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^4) \to \begin{aligned} & \Omega^{1,\bullet}(\C^4)\\ & \Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R^2).
\]

So far, we have only described how the fields of the $11$-dimensional theory behave upon dimensional reduction. 
One can rename the fields of the dimensionally reduced theory to match precisely with the fields of the conjectural minimal twist of  Type IIA supergravity with potentials $\mc E_{\rm pot}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2)$. 
In fact, we have the following stronger result, which identifies the interacting BV theories of the dimensionally reduced theory with the conjectural twist of Type IIA supergravity with potentials.

\begin{prop}
There is an equivalence of interacting classical BV theories on $\mb C^2 \times \mb R^2$
\[
\Psi : \oint_{S^1} \mc E_{11d} \to \mc E_{\rm pot} (\CC^4) \Hat{\otimes} \Omega^\bu(\mb R^2) 
\] 
defined on the fields by
\[
\arraycolsep=1.4pt\def\arraystretch{2.2}
\begin{array}{cccccccc}
\Psi (\mu_{01}) & = & \mu_{01} & \in & \PV^{1,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\
\Psi (\mu_{10}) & = & \Omega^{-1}_{\mb C^4} \vee \mu_{10} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\ 
\Psi(u \mu^0_{11d}) & = & u \mu^0_{11d} & \in & u \PV^{0,\bu} (\CC^4) \Hat{\otimes} \Omega^\bu (\RR^4) \\ 
\Psi (u^{-1} \gamma_{11d}^0) & = & u^{-1} \Omega^{-1}_{\CC^4} \vee \gamma_{11d}^0 & \in & u^{-1} \PV^{4,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) \\ \Psi(\gamma_{01}) &  = & \Omega^{-1}_{\CC^4} \vee \gamma_{01} & \in & \PV^{3,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) \\
\Psi (\gamma_{10}) & = & \gamma_{10} & \in & \PV^{0,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) .
\end{array} .
\]
\end{prop}

@@

%
%\begin{prop}
%There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\otimes\mc E_{Pot}$ given by
%\begin{itemize}
%\item $[\gamma_{10}]\mapsto\mu^0\in\PV^{0,\bullet}\subset\mc E_{Pot}$.
%  \item $[\mu_{01}]\mapsto\mu^1\in\PV^{1,\bullet}(\C^4)\subset\mc E_{Pot}$.
%\item $[\mu^{0}]\mapsto\mu^{c}\in\PV^{0, \bullet}(\C^{4})\subset\mc E_{Pot}$.
%\item $[\gamma_{01}]\mapsto\mu^3 = \gamma_{01}\vee\Omega^{-1}_{\C^4}\in\PV^{3,\bullet}\subset\mc E_{Pot}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
%\item $[\mu_{10}]\mapsto\mu^4 =\mu_{10}\vee\Omega^{-1}_{\C^4}\in\PV^{4,\bullet}\subset\mc E_{Pot}$ .
%
%
%\end{itemize}
%preserving the relevant pairings.
%\end{prop}

@@

%\begin{rmk}
%Note that the field $\mu^{c}\in \mc E_{\mr Pot}$ is nonpropating. It must pair against a field in $\PV^{3}$. In order for the field $\mu^{0}$ in M-theory to propagate, it must pair against a field $\gamma^{0}\in \Omega^{0,\bullet}$ which is the ghost for the gauge transformation for $\gamma^{1}$. This suggests an enlargement of $\mc E_{\mr Pot}$ where we add an additional field in $\PV^{3}$ which will be the image of the ghost of $\gamma^{1}$ in M-theory under dimensional reduction.
%\end{rmk}

%\surya{ When we discussewd dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$. I realized this was wrong - the resulting map cannot be a Lie map. Indeed, there is certainly a nontrivial bracket between $\gamma_{10}$ and $\gamma_{10}$ in M-theory, from expanding the $\gamma\del\gamma\del\gamma$ term. However, there is no nontrivial bracket between $\PV^{3,\bullet}$ and $\PV^{4,\bullet}$ in $\mc E_{\rm Pot}$ }
